\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{array}
    \usepackage{textcomp}
    \usepackage{varwidth}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}
    \usepackage[hidelinks]{hyperref}
    \hypersetup{
      colorlinks=false
    }
    \urlstyle{same}
    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
    \vspace*{-40pt}

    %==== Profile ====%
\vspace*{-10pt}
\begin{center}
  {\Huge \scshape {Oreoluwa Bimbo-Salami}}\\
  Lagos, Nigeria $\cdot$ \href{mailto:oreoluwabs25@gmail.com}{oreoluwabs25@gmail.com} $\cdot$ \href{tel:+234 8098010828}{+234 8098010828} $\cdot$ \url{https://oreoluwabs.com}\\
\end{center}

%==== Education ====%
      \header{Education}

      \textbf{Covenant University}\hfill Nigeria\\
B.Sc Computer Science \hfill 01/09/2016 - 17/10/2020\\

\vspace{2mm}

%==== Experience ====%
      \header{Work Experience}
      \vspace{1mm}

      \textbf{Spurt!}\\
          \textit{Product Development Associate} \hfill March 2022 - Present\\
          \vspace{-1mm}
\begin{itemize} \itemsep 1pt
      \item Developed user-friendly, responsive, and performant web applications for Spurt!, ensuring a seamless user experience and optimal performance. Implemented robust security measures to protect sensitive user data and maintain a secure environment.
      \item Improved user experience, accessibility, and load times of in-house products by implementing strategic design changes and performance optimizations, resulting in a significant 50\% increase in overall performance.
      \item Developed and executed strategic plans for the implementation of Sync! - a productivity management and talent acquisition tool at Spurt!, resulting in enhanced performance and user experience through effective collaboration with engineers and stakeholders.
      \item Developed and implemented key features including customer onboarding, product and team management, in-app messaging, and payments using Next.js (React), resulting in a seamless user experience and increased customer satisfaction for Spurt!'s platform.
\end{itemize}
      \textbf{Neukleos}\\
          \textit{Software Developer} \hfill April 2021 - Present\\
          \vspace{-1mm}
\begin{itemize} \itemsep 1pt
      \item Developed and implemented a book learning platform at Neukleos, resulting in a significant increase of 40\% in employee engagement and retention rates.
      \item Developed and implemented intuitive user interfaces by integrating REST APIs, ensuring seamless functionality and enhancing user experience for client projects and websites at Neukleos.
      \item Revamped and enhanced the user experience, accessibility, and load times of our in-house product, resulting in a remarkable 25\% overall performance gain and an impressive 80\% surge in positive client reviews.
      \item Developed and deployed user-friendly web applications for Neukleos, with a focus on optimizing mobile performance and enhancing overall user experience.
      \item Developed and maintained client-side state management systems using Zustand, Redux, and React Context, ensuring efficient data flow and seamless user experiences for Neukleos' web applications.
      \item Developed and implemented automated design tools using Figma, resulting in a 10\% reduction in design time for Neukleos.
\end{itemize}
      \textbf{Neukleos}\\
          \textit{Software Developer Intern} \hfill Jan 2019 - July 2019\\
          \vspace{-1mm}
\begin{itemize} \itemsep 1pt
      \item Collaborated with a cross-functional project team consisting of developers with diverse skill sets to drive innovation and develop cutting-edge tools and solutions for Neukleos' clients, resulting in enhanced client satisfaction and increased business opportunities.
      \item Developed responsive and user-friendly web applications using HTML5, CSS3, and JavaScript frameworks such as React, resulting in enhanced user experience and increased customer satisfaction.
      \item Developed and maintained client-side state management using Redux, ensuring efficient data flow and seamless user experience for Neukleos' web applications.
      \item Developed reusable front-end components using popular libraries such as Styled Components, Bootstrap, and custom tools, ensuring efficient and scalable development for future projects at Neukleos.
\end{itemize}

\header{Skills}
\begin{tabular}{V{5cm} @{\hskip 0.6cm} V{12cm}}
Languages: & JavaScript, TypeScript, SQL (Postgres/MySQL), HTML/CSS \\
Frameworks: & React(NextJS/Remix), Astro, Vue, Node.js, REST, GraphQL \\
Developer Tools: & Git, Docker, VS Code \\
Libraries: & TRPC, CSS-in-JS, Tailwind, Zustand \\
\end{tabular}
\vspace{2mm}

\header{Projects}
      {\textbf{Nodnot}} {\sl NextJS, TypeScript, IndexDB, Git} \hfill \url{https://nodnot.vercel.app}\\
A node based AI powered note taking application with a notion like experience with additional features such as Image uploads, web embeds, secure storage with indexDB\\
\vspace*{2mm}
      {\textbf{Tinissue}} {\sl Remix, TypeScript, MySQL, Git} \hfill \url{https://tinissue-production.up.railway.app}\\
A project management application for teams and personal used with robust analytics, team management, milestone management\\
\vspace*{2mm}

    \end{document}