%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Oreoluwa Bimbo-Salami} \\ \vspace{1pt}
    \small +234-809-801-0828 $|$ \href{mailto:oreoluwabs25@gmail.com}{\underline{oreoluwabs25@gmail.com}} $|$
    \href{https://linkedin.com/in/oreoluwa-bimbo-salami-a40a79199/}{\underline{linkedin.com/in/oreoluwa-bimbo-salami-a40a79199/}} $|$
    \href{https://github.com/oreoluwa-bs}{\underline{github.com/oreoluwa-bs}} $|$  \small Lagos, Nigeria
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Covenant University}{Nigeria}
      {Bachelor of Science in Computer Science}{2020}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
    {Web Consultant}{August 2024 -- Present}
    {Tangerine Africa} { }
    \resumeItemListStart
        \resumeItem{Led website development, including detailed audits, animations, and third-party integrations to enhance user experience and functionality.}
        \resumeItem{Managing external vendors, ensuring timely delivery, quality, and alignment with business goals.}
    \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer}{March 2022 -- Present}
      {Spurt!} { }
      \resumeItemListStart
        \resumeItem{Developed and implemented key features including customer onboarding, product and team management, in-app messaging, and payments using Next.js (React).}
        \resumeItem{Built internal tools to automate administrative and operations tasks amongst teammates. }
        % Implemented robust security measures to protect sensitive user data and maintain a secure environment.
        \resumeItem{Developed user-friendly, responsive, and performant web applications, ensuring a seamless user experience and optimal performance.}
        \resumeItem{Developed and executed strategic plans for the implementation of Sync! - a productivity management and talent acquisition tool at Spurt!.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{April 2021 -- Present}
      {Neukleos} { }
      \resumeItemListStart
        \resumeItem{Refactoring and upgrading legacy web applications for stock photos and sharing in the African space.}
        \resumeItem{Built a Figma plugin 'NodeConnect' to automate key visual resizing time by at least 10\%.}
        \resumeItem{Developed and implemented a book learning platform at Neukleos, resulting in a significant increase of 40\% in employee engagement and retention rates.}
        \resumeItem{Developed and implemented intuitive user interfaces by integrating REST APIs, ensuring seamless functionality and enhancing user experience for internal and client projects.}
        \resumeItem{Developed and maintained client-side state management systems using Zustand, Redux, and React Context, ensuring efficient data flow and seamless user experiences for web applications.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Developer Intern}{Jan 2019 -- July 2019}
      {Neukleos} { }
      \resumeItemListStart
        \resumeItem{Collaborated with a cross-functional project team consisting of developers with diverse skill sets to drive innovation and develop cutting-edge tools and solutions for clients, resulting in enhanced client satisfaction and increased business opportunities.}
        \resumeItem{Developed responsive and user-friendly web applications using HTML5, CSS3, and JavaScript frameworks such as React, resulting in enhanced user experience and increased customer satisfaction.}
        \resumeItem{Developed and maintained client-side state management using Redux, ensuring efficient data flow and seamless user experience for web applications.}
        \resumeItem{Built reusable front-end components using popular libraries such as Styled Components, Bootstrap, and custom tools, ensuring efficient and scalable development for future projects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Nodnot} $|$ \emph{NextJS, TypeScript, IndexDB, Git}}{\url{https://nodnot.vercel.app}}
          \resumeItemListStart
            \resumeItem{A local-first node-based AI-powered note-taking application with a notion-like experience with additional features such as Image uploads, web embeds, secure storage with indexDB}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Tinissue} $|$ \emph{Remix, TypeScript, MySQL, Git}}{\url{https://tinissue-production.up.railway.app}}
          \resumeItemListStart
            \resumeItem{A project management application for teams and personal used with robust analytics, team management, milestone management}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Rayleigh Methodist Church} $|$ \emph{PHP,WordPress}}{\url{https://rayleighmethodistchurch.org.uk/}}
          \resumeItemListStart
            \resumeItem{Developed and implemented a custom-built website for RMC. Utilized WordPress and wrote custom plugins to create a user-friendly and visually appealing platform. }
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, SQL (Postgres/MySQL), Golang, HTML/CSS} \\
     \textbf{Frameworks}{: React(NextJS/Remix), Astro, Vue, Node.js, REST, Laravel, GraphQL} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Zed,  AWS} \\
     \textbf{Libraries}{: TRPC, CSS-in-JS, Tailwind}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
