%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Oreoluwa Bimbo-Salami} \\ \vspace{1pt}
    \small +234-809-801-0828 $|$ \href{mailto:oreoluwabs25@gmail.com}{\underline{oreoluwabs25@gmail.com}} $|$
    \href{https://linkedin.com/in/oreoluwa-bimbo-salami-a40a79199/}{\underline{linkedin.com/in/oreoluwa-bimbo-salami-a40a79199/}} $|$
    \href{https://github.com/oreoluwa-bs}{\underline{github.com/oreoluwa-bs}} $|$  \small Lagos, Nigeria
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
    {Fullstack Engineer}{January 2026}
    {Benmore Technologies} { }
    \resumeItemListStart
        \resumeItem{Designed and deployed backend systems for a 2-sided marketplace, handling transactional workflows, state consistency, and payment orchestration.}
        \resumeItem{Integrated payments infrastructure customer billing, provider payouts, transaction flows}
    \resumeItemListEnd

    \resumeSubheading
    {Frontend Engineer (Contract)}{August 2024 -- January 2026}
    {Tangerine Africa} { }
    \resumeItemListStart
        \resumeItem{Engineered payments, claims automation, and premium-calculation systems, reducing manual processing time.}
        \resumeItem{Improved system-level performance by 35\% by redesigning rendering strategy (SSR/SSG), optimizing data-fetching paths and reducing client-server round trips.}
        \resumeItem{Integrated Payload CMS and analytics tooling to empower marketing teams and accelerate content updates.}
        \resumeItem{Led frontend development, audits, animations, and vendor management to align UX with business goals.}
    \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer (Contract)}{March 2022 -- Present}
      {Spurt!} { }
      \resumeItemListStart
        \resumeItem{Developed and implemented key features including customer onboarding, product and team management, in-app messaging, and payments using Next.js (React).}
        \resumeItem{Built internal automation tools to streamline operational workflows, reducing manual coordination and improving system reliability across team processes.}
        % \resumeItem{Built internal tools to automate administrative and operations tasks amongst teammates. }
        % Implemented robust security measures to protect sensitive user data and maintain a secure environment.
        \resumeItem{Developed user-friendly, responsive, and performant web applications, ensuring a seamless user experience and optimal performance.}
        \resumeItem{Led end-to-end implementation of a productivity platform, defining frontend architecture, data models from concept to production.}
    \resumeItemListEnd

    \resumeSubheading
      {Frontend Engineer (Full-Time)}{January 2025 -- September 2025}
      {Rvysion!} { }
      \resumeItemListStart
        \resumeItem{Implemented onboarding and compliance systems with complex validation and multi-step workflows, ensuring correctness across user state transitions and regulatory constraints.}
        % \resumeItem{Developed onboarding, business name, company registration and compliance management features for law-tech systems using React.}
        \resumeItem{Developed user-friendly, responsive, and performant web applications, ensuring a seamless user experience and optimal performance.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer (Full-Time)}{April 2021 -- September 2025}
      {Neukleos} { }
      \resumeItemListStart
        \resumeItem{AArchitected and launched a SaaS LMS platform from concept to production, designing system architecture, data models, and scalable backend services supporting multi-tenant usage, unlocking new B2B revenue streams.}
        \resumeItem{Refactored and modernized legacy applications for creative and media clients across Africa.}
        \resumeItem{Built 'NodeConnect' Figma plugin automating design resizing and improving productivity by 10\%.}
        \resumeItem{Architected and deployed a book-learning platform that increased engagement by 40\% through gamification.}
        \resumeItem{Integrated backend services with frontend systems and implemented observability (Sentry) to detect, trace, and resolve production issues proactively.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Developer (Internship) }{Jan 2019 -- July 2019}
      {Neukleos} { }
      \resumeItemListStart
        \resumeItem{Collaborated with multi-disciplinary teams to deliver modern React-based applications for clients.}
        \resumeItem{Developed responsive and user-friendly web applications using HTML5, CSS3, and JavaScript frameworks such as React, resulting in enhanced user experience and increased customer satisfaction.}
        \resumeItem{Developed and maintained client-side state management using Redux, ensuring efficient data flow and seamless user experience for web applications.}
        \resumeItem{Built reusable front-end components using popular libraries such as Styled Components, Bootstrap, and custom tools, ensuring efficient and scalable development for future projects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Two Threads} $|$ \emph{React, TypeScript, Postgres, Go, Git}}{\url{https://twothreads.app}}
          \resumeItemListStart
            \resumeItem{An app that keeps track of what you own, helps you decide what to wear, and recommends what to buy next — powered by an AI style assistant leveraging LLM-based inference to generate personalized suggestions from user-owned inventory.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Zoop} $|$ \emph{Golang}}{\url{https://github.com/oreoluwa-bs/zoop}}
          \resumeItemListStart
            \resumeItem{A fast, minimal CLI for storing and retrieving you store and retrieve anything—API keys, passwords, tokens, notes, secrets}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{StudyBuddy} $|$ \emph{React, TypeScript, SQLite, Git}}{\url{https://studybuddy.almosteverything.app}}
          \resumeItemListStart
            \resumeItem{Built an AI-powered study assistant that processes user-uploaded materials and delivers structured explanations, adaptive quizzes, and optimized study plans.}
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Tinissue} $|$ \emph{Remix, TypeScript, MySQL, Git}}{\url{https://tinissue-production.up.railway.app}}
      %     \resumeItemListStart
      %       \resumeItem{A project management application for teams and personal used with robust analytics, team management, milestone management}
      %     \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Nodnot} $|$ \emph{NextJS, TypeScript, IndexDB, Git}}{\url{https://nodnot.vercel.app}}
      %     \resumeItemListStart
      %       \resumeItem{A local-first node-based AI-powered note-taking application with a notion-like experience with additional features such as Image uploads, web embeds, secure storage with indexDB}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: React (Next.js, Remix, Astro), Vue, TypeScript, Chakra UI, Tailwind, Zustand, Redux} \\
     \textbf{Backend}{: Node.js(Express), Golang, REST/GraphQL, tRPC, SQL(Postgres/MySQL)} \\
     \textbf{Infrastructure}{: Docker, AWS, CI/CD (GitHub Actions), Sentry, Payload CMS} \\
     \textbf{Testing}{: Jest, Vitest, Cypress, Playwright} \\
     \textbf{Tools}{: Git, Zed, VS Code} \\
    }}
 \end{itemize}


 %-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
    {Covenant University}{Nigeria}
    {Bachelor of Science in Computer Science}{2020}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
